CopyKAT CNV results exploration for `r params$sample_id`

### 2024-11-15 analyses/cell-type-wilms-tumor-06/notebook_template/05_copykat_exploration.Rmd
fix typos on 05 notebook, but do not regenerate

---
title: "Copykat CNV results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  sample_id: "SCPCS000179"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

From the heatmap of CNV and the mean CNV detection plots, there does not appear to be any pattern that drives the identification of aneuploid cells. 
The assignment of the aneuploidy/diploidy value might relies on very few CNV and/or an arbitrary threshold. 
This might be why the assignement of aneuploidy/diploidy values differs between condition (and between runs!!).

>>>>

---
title: "CopyKAT CNV results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  sample_id: "SCPCS000179"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

From the heatmap of CNV and the mean CNV detection plots, there does not appear to be any pattern that drives the identification of aneuploid cells. 
The assignment of the aneuploidy/diploidy value might relies on very few CNV and/or an arbitrary threshold. 
This might be why the assignment of aneuploidy/diploidy values differs between condition (and between runs!!).
